Supporting Information

### 2016-08-16 portfolio/analysis/1-create-modelling-data.Rmd
Keep track of sample sizes during filtering

---
title: "Create data sets for modeling"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
---

@@

# remove white space in 2nd position
idx = which(substr(cfec$p_fshy, 2, 2) == " ")
cfec$p_fshy[idx] = paste(substr(cfec$p_fshy[idx], 1, 1),
  substr(cfec$p_fshy[idx], 3, length(cfec$p_fshy[idx])), sep="")

@@

dim(cfecnew)[1]
```

@@

permit_rev = group_by(cfecnew, p_holder, year, p_fshy) %>%
  summarize(permit.rev = sum(g_earn)) %>%
  as_data_frame() %>%
  group_by(p_holder, year) %>%
  mutate(tot.rev = sum(permit.rev))
permit_rev$permit.rev = permit_rev$permit.rev/permit_rev$tot.rev # fraction of total
permit_rev = permit_rev[permit_rev$permit.rev < 0.1,]

# Delete these minimal earnings
nrow(cfecnew)
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_fshy) %in% 
  paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_fshy)), ]
nrow(cfecnew)

@@

```{r}
# make sure the data are tidy:
cfecAnnual <- as_data_frame(cfecAnnual)

## Filtering out people with 10+ years of fishing. Drops rows from 13.7 to 10 million.
## (now doing this at the beginning of the modeling scripts)
# cfecAnnual = group_by(cfecAnnual, p_holder) %>%
#   mutate(nyr = length(unique(year))) %>%
#   filter(nyr >= 10)

@@

cfecAnnual$specDiv.change = cfecAnnual$specDiv - cfecAnnual$specdiv.prev
cfecAnnual.diff = cfecAnnual[is.na(cfecAnnual$specDiv.change)==FALSE, ]
saveRDS(cfecAnnual.diff, file="portfolio/data-generated/cfec-diff-for-modeling.rds")
```

>>>>

---
title: "Create data sets for modeling"
output:
  pdf_document:
    fig_caption: yes
---

@@

# remove white space in 2nd position
idx = which(substr(cfec$p_fshy, 2, 2) == " ")
cfec$p_fshy[idx] = paste(substr(cfec$p_fshy[idx], 1, 1),
  substr(cfec$p_fshy[idx], 3, length(cfec$p_fshy[idx])), sep="")
```

@@

dim(cfecnew)[1]
ndat <- list()
ndat$initial <- nrow(cfecnew)
```

@@

permit_rev = group_by(cfecnew, p_holder, year, p_fshy) %>%
  summarize(permit.rev = sum(g_earn)) %>%
  as_data_frame() %>%
  group_by(p_holder, year) %>%
  mutate(tot.rev = sum(permit.rev))
permit_rev$permit.rev = permit_rev$permit.rev/permit_rev$tot.rev # fraction of total
ndat$rev_b4_10perc <- sum(permit_rev$permit.rev)
permit_rev = permit_rev[permit_rev$permit.rev < 0.1,]
ndat$rev_after_10perc <- sum(permit_rev$permit.rev)

# Delete these minimal earnings
nrow(cfecnew)
ndat$before_10_perc <- nrow(cfecnew)
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_fshy) %in% 
  paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_fshy)), ]
nrow(cfecnew)
ndat$nrow_over_10_perc <- nrow(cfecnew)

@@

```{r}
# make sure the data are tidy:
cfecAnnual <- as_data_frame(cfecAnnual)
ndat$annual <- nrow(cfecAnnual)

@@

cfecAnnual$specDiv.change = cfecAnnual$specDiv - cfecAnnual$specdiv.prev
cfecAnnual.diff = cfecAnnual[is.na(cfecAnnual$specDiv.change)==FALSE, ]
saveRDS(cfecAnnual.diff, file="portfolio/data-generated/cfec-diff-for-modeling.rds")
ndat$annual_diff <- nrow(cfecAnnual.diff)
saveRDS(ndat, file = "portfolio/data-generated/ndat.rds")
```

### 2016-08-16 portfolio/text/supp.Rnw
Develop text
Keep track of sample sizes during filtering

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabu} % for spacing between rows in longtable
\usepackage{url}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\modulolinenumbers[2]

@@

\mathchardef\mhyphen="2D % math hyphen

@@

@@

Rows of data: \Sexpr{nrows}.
Number of permit holders: \Sexpr{npholders}.
Range of years: \Sexpr{range_yrs}.
Number of strategies: \Sexpr{nstr}

\citep{gelman2014}

@@

@@

\subsection{points to include}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{url}
\usepackage{mathtools}
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\modulolinenumbers[2]

@@

@@

\section{Data filtering}

<<nothing, eval=FALSE>>=
permit_rev = group_by(cfecnew, p_holder, year, p_fshy) %>%
  summarize(permit.rev = sum(g_earn)) %>%
  as_data_frame() %>%
  group_by(p_holder, year) %>%
  mutate(tot.rev = sum(permit.rev))
permit_rev$permit.rev = permit_rev$permit.rev/permit_rev$tot.rev # fraction of total
permit_rev = permit_rev[permit_rev$permit.rev < 0.1,]

# Delete these minimal earnings
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_fshy) %in%
  paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_fshy)), ]

cfecnew <- filter(cfecnew, p_spec != "Freshwater") # only 1400 rows
@

Rows of data initial: \Sexpr{round(ndat$initial/1e6,2)} million

Rows of data annual: \Sexpr{ndat$annual}

Rows of data diff: \Sexpr{ndat$annual_diff}

% \Sexpr{ndat$rev_b4_10perc/1e9}
% \Sexpr{round(ndat$rev_after_10perc/1e9,2)}

\Sexpr{ndat$before_10_perc}

Rows of data after 10,000 cull: \Sexpr{ndat$large_only}

10,000 cull: rev:
\Sexpr{round(1-ndat$rev_large_only/ndat$rev_b4_large_only,2)*100}

\Sexpr{round(ndat$rev_large_only/1e9,2)}

\section{Assigning strategies}

\Sexpr{nstrat$enough_pholders}

\Sexpr{round(ndat$rev_enough_pholders/1e9,2)}

\Sexpr{nstrat$no_river_exp}

\Sexpr{round(ndat$rev_no_river_exp/1e9,2)}

Number of strategies: \Sexpr{nstr}

Rows of data before no singles: \Sexpr{ndat$before_nosingles}

% \Sexpr{ndat$b4_no_na_strat}
%
% \Sexpr{ndat$rev_b4_no_na_strat}
%
% \Sexpr{ndat$after_no_na_strat}

lost \% rev no strat:
\Sexpr{round(ndat$rev_after_no_na_strat/ndat$rev_b4_no_na_strat,2)*100}

lost rows no strat:
\Sexpr{round(ndat$after_no_na_strat/ndat$b4_no_na_strat,2)*100}

% \Sexpr{ndat$rev_after_no_na_strat}
%
% \Sexpr{ndat$rev_final}

Rows of data: \Sexpr{ndat$final}

Number of permit holders: \Sexpr{npholders}

Range of years: \Sexpr{range_yrs}

Number of strategy-years: \Sexpr{nstr_yrs}

@@

Overview... why first diff, why 2 part

@@

\citep{gelman2014}
\citep{rcoreteam2016}

@@
